Exploring dimensions of biodiversity in Japanese ferns

### 2020-06-30 ms/SI.Rmd
Update SI
- add function for automatically generating results files based on caption name
- add raw and SES diversity biplots

phylo_cache <- new_cache(here::here("phylo_cache"))

loadd(list = c(
  "plastome_calibration_dates",
  "plastome_tree"
),
cache = phylo_cache)

@@

@@

ggsave(here::here("results/Fig_S1.pdf"), width = 7, height = 6, units = "in")
```

@@

```{r biplots}

loadd(ses_phy_ferns, cache = ja_fern_cache)
loadd(ses_traits_ferns, cache = ja_fern_cache)
loadd(shape_ferns, cache = ja_fern_cache)

# Helper function for making a scatterplot
scatterplot <- function(data, x_var, y_var, x_lab, y_lab) {
  ggplot(data, aes(x = .data[[x_var]], y = .data[[y_var]])) +
    geom_point(alpha = 0.5) +
    labs(
      x = x_lab,
      y = y_lab
    )
}

# Join data
ses_comp <-
ses_phy_ferns %>%
  select(site, mpd_obs, pe_obs, mpd_obs_z, pe_obs_z) %>%
  left_join(
    select(ses_traits_ferns, site, mpd_morph_obs, mpd_morph_obs_z),
    by = "site"
  ) %>%
  left_join(
    as_tibble(shape_ferns) %>% select(site = grids, richness),
    by = "site"
  )

# Raw metrics ----

@@

# Make plot
pmap(raw_comparisons, scatterplot, data = ses_comp) %>%
wrap_plots() +
  plot_annotation(tag_levels = 'A')

# SES metrics ----

@@

# Make plot
pmap(ses_comparisons, scatterplot, data = ses_comp) %>%
  wrap_plots() +
  plot_annotation(tag_levels = 'A')
```

>>>>

@@

ggsave(result_file("k-plot", "pdf"), width = 7, height = 3, units = "in")
```

@@

ggsave(result_file("endemism-restricted", "pdf"), width = 7, height = 6, units = "in")
```

@@

```{r biplot-prep}
# Helper function for making a scatterplot
scatterplot <- function(data, x_var, y_var, x_lab, y_lab) {
  ggplot(data, aes(x = .data[[x_var]], y = .data[[y_var]])) +
    geom_point(alpha = 0.5) +
    labs(
      x = x_lab,
      y = y_lab
    )
}

```{r raw-biplot, fig.width = 7, fig.height = 6}
## Biplots of raw metrics ##

@@

# Make plot
pmap(raw_comparisons, scatterplot, data = ses_div_ferns_spatial) %>%
wrap_plots() +
  plot_annotation(tag_levels = 'A')

ggsave(result_file("raw-biplot", "pdf"), width = 7, height = 6, units = "in")
```

**`r s_figure("raw-biplot")`**. `r s_figure_cap("raw-biplot")` MPD, mean phylogenetic distance; MMD, mean morphological distance; PE, phylogenetic endemism.

```{r ses-biplot, fig.width = 7, fig.height = 6}
## Biplots of SES metrics ##

@@

# Make plot
pmap(ses_comparisons, scatterplot, data = ses_div_ferns_spatial) %>%
  wrap_plots() +
  plot_annotation(tag_levels = 'A')

ggsave(result_file("ses-biplot", "pdf"), width = 7, height = 6, units = "in")
```

**`r s_figure("ses-biplot")`**. `r s_figure_cap("ses-biplot")` MPD, mean phylogenetic distance; MMD, mean morphological distance; PE, phylogenetic endemism.
